An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-08-03 poly-embed-journal/poly-embed-journal.tex
intro and comments/edits here and there

Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}\jessiet{I took dimension of the hypothesis space to be, e.g., the degree of the polynomial $k$ for $\H = \{h : |\X| \times k \to \reals\}$.  Not sure if we should change to surrogates prediction/report space?}\raft{Excellent point.  Changed to prediction dimension, with a bit of explanation.}
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.

\bo{This is pretty inaccessible to nonexperts. I think we should consider a rewrite that expands this intro and makes it much more accessible. For example what is a surrogate? It would help many readers a lot to spell things out more.}
We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If this embedding can be extended to a calibrated link function, which roughly maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.

\raf{The old intro had just one more paragraph here, now commented out}
% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.

@@

A first observation is that a loss restricted to some representative set $\Sc$ elicits the same property restricted to $\Sc$.
As a consequence, restricting to representative sets preserves the Bayes risk.
We will use these observations throughout.
\begin{lemma}\label{lem:loss-restrict}
  Let $L:\R\to\reals^\Y_+$ elicit $\Gamma$, and let $\Sc\subseteq\R$ be representative for $L$.
  % such that $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in\simplex$.
  Then $L|_\Sc$ elicits $\gamma:\simplex\toto\Sc$ defined by $\gamma(p) = \Gamma(p)\cap \Sc$.
  Moreover, $\risk{L}=\risk{L|_\Sc}$.
\end{lemma}
\bo{I didn't see us define $L|_\Sc$ anywhere yet! Although it's briefly mentioned in the intro.}
\bo{Notation in the lemma is confusing because $L$ is supposed to be a surrogate with report space $\reals^d$ and $\R$ is supposed to be the report space for $\ell$.}
\begin{proof}
  Let $p\in\simplex$ be fixed throughout.
  First let $r \in \gamma(p) = \Gamma(p) \cap \Sc$.
  Then $r \in \Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$, so as $r\in\Sc$ we have in particular $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  For the other direction, suppose $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  As $\Sc$ is representative for $L$, we must have some $s \in \Gamma(p) \cap \Sc$.
  On the one hand, $s\in\Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$.
  On the other, as $s \in \Sc$, we certainly have $s \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(s)}$, and thus $r \in \argmin_{u\in\R} \inprod{p}{L(u)} = \Gamma(p)$ as well.
  We now see $r \in \Gamma(p) \cap \Sc$.
  Finally, the equality of the Bayes risks $\min_{u\in\R} \inprod{p}{L(u)} = \min_{u\in\Sc} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\Sc \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

@@

While we have focused on polyhedral losses thus far, it turns out that many of our results about embeddings extend to losses with polyhedral Bayes risks.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, \jessie{Would a figure be helpful?} which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.

@@

	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.\jessie{This is a different $\Sc$ than the first paragraph, right? The first $\Sc$ is representative for $\ell$.}
  As $\R^*$ and $\Sc$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\Sc)|=\Sc$.
  We conclude that $\R^*$ and $\Sc$ are both in bijection with $\V$.
  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = s \in \Sc$ where $\ell(r) = L(s)$, is therefore well-defined.
  Condition (i) of an embedding is immediate.
  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_\Sc$, both via the identity embedding.
  Using condition (ii) from both embeddings, for all $p\in\simplex$ and $r\in\R^*$, we have
  \begin{equation*}
    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_\Sc}(p)
    \iff \varphi(r) \in \prop{L}(p)~,
  \end{equation*}
  giving condition (ii).
\end{proof}

@@

Central to the structural results in Lemma~\ref{lem:X} is the existence of a canonical set of loss vectors $\V$ which match the loss vectors of any minimum representative set.
This fact may seem surprising when one considers that losses may have many mimimum representative sets.
For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L(r)_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$. \jessie{Do we want this as an example or is it too contrived? I don't have a better one though.  We could also point out that lots of surrogates have an extra dimension in practice (e.g., people use $n$ dimensions instead of $n-1$ for multiclass classification.)}
Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.

@@

The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}\raft{TODO: see if there are other references we should include here.  Maybe Jessie you could search? \jessie{Quick search leads me to a couple of your papers and Nico's, but not much else.}}.
Intuitively, a loss is non-redundant if no report is weakly dominated by another report.

@@

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessie{$\reals^d$ vs $\R$?}
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\hat\Theta$ of $\Gamma$, and $\cup\,\hat\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
\end{proposition}

@@

  Case 2:
  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \R\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$. \jessie{Technically, $\R$ not defined?}
  As $\Gamma$ is elicitable, $\R$ is representative for $\Gamma$.
  By definition of $\trimred$, we have $\simplex = \cup_{r\in\R} \Gamma_r \subseteq \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$. \jessie{I'm a bit confused by this- how do we get $\cup_{\R}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}
  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ \jessie{$\R$?} for $L$ and $\Gamma$, showing Case 3.
  Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  \jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.  However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.  Once we have $\Sc$ a finite representative set, we can apply Lemma X to say it also contains a finite \emph{minimum} rep set.}

@@

  Case 4:
  Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
  Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$. \jessie{$\Gamma$?}
  %
  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
  %
  % 
  % It remains to show $\trimred(\gamma) = \Theta$.
  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
  % 
  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
\end{proof}

@@

  Fix $p \in \simplex$.
  \begin{align*}
    p \in \theta(v)
    &\iff \inprod{v}{p} = f(p) & \text{Def of $\theta$}\\
    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f$ matches $g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex}.)}\\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} & \text{Def of argmin}\\
    &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
  \end{align*}
\end{proof}

\begin{claim}\label{claim:level-set-is-projected-face}
  For all $r \in \R$ with $v = L(r)$, $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
\end{claim}
\begin{proof}
  % Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
  Let us rewrite
  \begin{align*}
    \Gamma_r
    &= \{p \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\}\\
    &= \{p \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
    &= \theta(v)
  \end{align*}
  Now, we have $p \in \theta(v)$ if and only if,
  \begin{align*}
    p \in \theta(v)
    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {Since $f = g$ on simplex} \\
    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
    &\iff p \in \pi(F_v) \cap \simplex & \text{Following from definition of $F_v$}
  \end{align*}
  The result follows.

@@

\begin{lemma}\label{lem:levelset-to-extended-levelset}
  For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
\end{lemma}
\begin{proof}
  Fix $r \in \R$ and $c > 0$.
  We have
  \begin{align*}
    p \in \Gamma_r
    &= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Def of level set} \\
    &= \{p' \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p'} \} & \text {$\V = L(\R)$} \\
    &= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in \V} \inprod{v'}{p'} \} & \text {$L$ minnable} \\
    &= \{p' \in \simplex \mid \inprod{v}{p'} = g(p') \} & \text {Definition of $g$} \\
    &= \{p' \in \simplex \mid c \inprod{v}{p'} = g(p') \} & \text {Multiplying both sides by $c$} \\
    &= \{p' \in \simplex \mid  \inprod{v}{cp'} = g(cp') \} & \text {Linearity of inner product and Lemma~\ref{lem:g-1-homog}} \\
    \implies cp
    &\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\}\\
    &= \bar \Gamma_r
  \end{align*}
\end{proof}

>>>>

In supervised learning, one tries to learn a hypothesis which fits some labeled data, as judged by a target loss function.
Unfortunately, minimizing the target loss directly is typically computationally intractable, especially for discrete prediction tasks like classification, ranking, and structured prediction.
Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
Given a surrogate hypothesis, a link function then translates back to the target problem.
This general approach, called surrogate risk minimization, is ubiquitous in supervised machine learning algorithms.
\botodo{This is pretty inaccessible to nonexperts. I think we should consider a rewrite that expands this intro and makes it much more accessible. For example what is a surrogate? It would help many readers a lot to spell things out more.}
\raft{I added this paragraph (based on our rates paper) and then transitioned into the next}

% Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If this embedding can be extended to a calibrated link function, which roughly maps approximately $L$-optimal reports to $\ell$-optimal reports, then consistency follows~\citep{agarwal2015consistent}.
Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.

% OLD INTRO PARAGRAPH:
% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.

@@

A first observation is that a loss restricted to some representative set $\Sc$ elicits the same property restricted to $\Sc$.
As a consequence, restricting to representative sets preserves the Bayes risk.
We will use these observations throughout.
\begin{lemma}\label{lem:loss-restrict}
  Let $L:\R\to\reals^\Y_+$ elicit $\Gamma$, and let $\Sc\subseteq\R$ be representative for $L$.
  % such that $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in\simplex$.
  Then $L|_\Sc$ elicits $\gamma:\simplex\toto\Sc$ defined by $\gamma(p) = \Gamma(p)\cap \Sc$.
  Moreover, $\risk{L}=\risk{L|_\Sc}$.
\end{lemma}
\botodo{I didn't see us define $L|_\Sc$ anywhere yet! Although it's briefly mentioned in the intro.}\raft{Yeah, maybe recall the def here?}
\botodo{Notation in the lemma is confusing because $L$ is supposed to be a surrogate with report space $\reals^d$ and $\R$ is supposed to be the report space for $\ell$.}\raft{We should discuss this point}
\begin{proof}
  Let $p\in\simplex$ be fixed throughout.
  First let $r \in \gamma(p) = \Gamma(p) \cap \Sc$.
  Then $r \in \Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$, so as $r\in\Sc$ we have in particular $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  For the other direction, suppose $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  As $\Sc$ is representative for $L$, we must have some $s \in \Gamma(p) \cap \Sc$.
  On the one hand, $s\in\Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$.
  On the other, as $s \in \Sc$, we certainly have $s \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(s)}$, and thus $r \in \argmin_{u\in\R} \inprod{p}{L(u)} = \Gamma(p)$ as well.
  We now see $r \in \Gamma(p) \cap \Sc$.
  Finally, the equality of the Bayes risks $\min_{u\in\R} \inprod{p}{L(u)} = \min_{u\in\Sc} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\Sc \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

@@

While we have focused on polyhedral losses thus far, it turns out that many of our results about embeddings extend to losses with polyhedral Bayes risks.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$, \jessiet{Would a figure be helpful?}\raft{Yeah!} which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.

@@

	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\Sc \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\Sc)$.\jessiet{This is a different $\Sc$ than the first paragraph, right? The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}
  As $\R^*$ and $\Sc$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\Sc)|=\Sc$.
  We conclude that $\R^*$ and $\Sc$ are both in bijection with $\V$.
  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = s \in \Sc$ where $\ell(r) = L(s)$, is therefore well-defined.
  Condition (i) of an embedding is immediate.
  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_\Sc$, both via the identity embedding.
  Using condition (ii) from both embeddings, for all $p\in\simplex$ and $r\in\R^*$, we have
  \begin{equation*}
    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_\Sc}(p)
    \iff \varphi(r) \in \prop{L}(p)~,
  \end{equation*}
  giving condition (ii).
\end{proof}

@@

Central to the structural results in Lemma~\ref{lem:X} is the existence of a canonical set of loss vectors $\V$ which match the loss vectors of any minimum representative set.
This fact may seem surprising when one considers that losses may have many mimimum representative sets.
For example, consider hinge loss with a spurious extra dimension, i.e., $L:\reals^2\to\reals^\Y$, $L(r)_y = \max(0,1-r_1y)$ for $\Y = \{-1,+1\}$.
Here the minimum representative sets are $\{(-1,a),(1,b)\}$ for any $a,b\in\reals$. \jessiet{Do we want this as an example or is it too contrived? I don't have a better one though.  We could also point out that lots of surrogates have an extra dimension in practice (e.g., people use $n$ dimensions instead of $n-1$ for multiclass classification.)}\raft{I like the example for its simplicity.  We could add a footnote about this coming up in practice, but since it's not a major point I'd lean leaving it as-is. If you agree feel free to burn.}
Lemma~\ref{lem:X}(\ref{item:X-min-V}) states that, while the minimum representative set is not unique, its loss vectors are.

@@

The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}.
Intuitively, a loss is non-redundant if no report is weakly dominated by another report.

@@

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.  Probably don't... in any case, can't use $\R$ since that clashes with $\gamma$.}
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\hat\Theta$ of $\Gamma$, and $\cup\,\hat\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
\end{proposition}

@@

  Case 2:
  \raf{Somehow I had like 5 typos in here which made it impossible to follow.  Hopefully better now!}
  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
  As $\Gamma$ is elicitable, $\reals^d$ is representative for $\Gamma$.
  By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, showing Case 3.
  Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  \jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.  However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.  Once we have $\Sc$ a finite representative set, we can apply Lemma X to say it also contains a finite \emph{minimum} rep set.}

@@

  Case 4:
  Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
  Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
  %
  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
  %
  % 
  % It remains to show $\trimred(\gamma) = \Theta$.
  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
  % 
  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
\end{proof}

@@

  Fix $p \in \simplex$.
  \begin{align*}
    p \in \theta(v)
    &\iff \inprod{v}{p} = f(p) & \text{Definition of $\theta$}\\
    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f=g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})}\\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} &\\
    &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
  \end{align*}
\end{proof}

\begin{claim}\label{claim:level-set-is-projected-face}
  For all $r \in \R$ with $v = L(r)$, $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
\end{claim}
\begin{proof}
  % Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
  Let us rewrite
  \begin{align*}
    \Gamma_r
    &= \{p \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\}\\
    &= \{p \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
    &= \theta(v)
  \end{align*}
  \raf{Wait, isn't this just Claim 19 again?}
  Now, we have $p \in \theta(v)$ if and only if,
  \begin{align*}
    p \in \theta(v)
    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {$f = g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex})} \\
    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex & \\
    &\iff p \in \pi(F_v) \cap \simplex & \text{Definition of $\pi$, $F_v$}
  \end{align*}
  The result follows.

@@

\begin{lemma}\label{lem:levelset-to-extended-levelset}
  For any $r \in \R$ and $c > 0$, if $p \in \Gamma_r$, then $cp \in \bar \Gamma_r$. 
\end{lemma}
\begin{proof}
  Fix $r \in \R$ and $c > 0$.
  We have
  \begin{align*}
    p \in \Gamma_r
    &= \{p' \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p'} \} & \text {Definition of level set} \\
    &= \{p' \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p'} \} & \text {$\V = L(\R)$} \\
    &= \{p' \in \simplex \mid \inprod{v}{p'} = \min_{v' \in \V} \inprod{v'}{p'} \} & \text {$L$ minnable} \\
    &= \{p' \in \simplex \mid \inprod{v}{p'} = g(p') \} & \text {Definition of $g$} \\
    &= \{p' \in \simplex \mid c \inprod{v}{p'} = c g(p') \} &  \\
    &= \{p' \in \simplex \mid  \inprod{v}{cp'} = g(cp') \} & \text {Lemma~\ref{lem:g-1-homog}} \\
    \implies cp
    &\in \{x \in \reals^\Y_+ \mid \inprod{v}{x} = g(x)\}\\
    &= \bar \Gamma_r
  \end{align*}
\end{proof}
